### 2014-11-03 evaluation.tex
edits

Both \name and SC ensure correctness. However, with 512 clients, \name
implementation was within 30\% of latency and 12\% of throughput of EC, whereas
SC operations had 162\% higher latency and 52\% lower throughput than EC
operations. In \cf{2DC} configuration (not-shown), the average latency of SC
operations with 512 clients increased by 9.4$\times$ due to the cost of
geo-distributed coordination, whereas \name operations were only 2.2$\times$
slower, mainly due to the increased cost of \cf{withdraw} operations.
Importantly, the latency of \cf{getBalance} and \cf{deposit} remained almost
the same. This illustrates the benefit of fine-grained contract classification
in \name.

>>>>

Both \name and SC ensure correctness. However, with 512 clients, \name
implementation was within 41\% of latency and 18\% of throughput of EC, whereas
SC operations had 162\% higher latency and 52\% lower throughput than EC
operations. In \cf{2DC} configuration (not-shown), the average latency of SC
operations with 512 clients increased by 9.4$\times$ due to the cost of
geo-distributed coordination, whereas \name operations were only 2.2$\times$
slower, mainly due to the increased cost of \cf{withdraw} operations.
Importantly, the latency of \cf{getBalance} and \cf{deposit} remained almost
the same. This illustrates the benefit of fine-grained contract classification
in \name.
